Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-04-06 article/article.Rmd
+ discussion edits + add in tests to surrogacy stuff

## Discussion
We aimed to investigate the effectiveness of environmental and geographic surrogates for adaptive and neutral genetic variation in conservation planning. Our study is the first to test this in a multi-species context. Overall, we found that environmental and geographic variables are not necessarily effective surrogates for genetic variation in conservation planning--though they can be useful to for identifying suitable amount-based targets. Additionally, we found that surrogate-based targets can supplement amount-based targets and improve the proportion of neutral variation secured in a prioritization if the amount-based targets are too low. Our results suggest that in most cases--barring extremely unusual spatial patterns of intra-specific genetic variation--conservation planners can secure sufficient adaptive and neutral variation by following conventional guidelines.

### Single + multi-species analysis
* summarize results

* compare + contrast with other papers

* implication of results

### Correlation analysis
* summarize results

* compare + contrast with other papers

* implication of results

### Limitations/Future directions
We wish to alert our readers to several limitations associated with our analysis. First, the size of the planning units we used (23 $\times$ 25 km) is much larger than typically used in conservation planning scenarios (approx. 1--5 km^2). We used this resolution because the genetic data was collected at this scale. Whilst we could have interpolated the genetic data to a finer resolution and used smaller planning units, this would have biased our analysis because this process would have introduced artificial spatial auto-correlation into the dataset. Second, we used geographic distances as surrogates for connectivity between planning units. Although connectivity between areas can be modeled using isolation by resistance measures [@r473] derived from landscape data [eg. @r474], they are unlikely to be of use in broad-scale conservation exercises since they need to be tuned using species-specific parameters. Third, we used AFLP data to characterize the main gradients of genetic variation. Whilst next-generation sequencing provides higher resolution genetic information than AFLP data [reviewed in @r480], our methodology would still have utilized only the main gradients of the genetic variation in order to generate prioritizations in a feasible amount of time. Overall, we are confident that the limitations associated with our study are relatively minor.

>>>>

## Discussion
<!-- introduction -->
We aimed to investigate the effectiveness of broad-scale environmental and geographic variables as surrogates for adaptive and neutral genetic variation in conservation planning. Our study is the first to address this hypothesis using moderately realistic planning scenarios. Overall, we found that environmental and geographic variables are effective surrogates for a few species when developing prioritizations. Furthermore, when developing prioritizations under various planning scenarios, we found that the addition of environmental and geographic targets resulted in prioritizations that sufficiently represented the genetic variation of a greater number of species. Our results suggest that while the environmental and geographic variables have little benefit for most species, they can make a large difference for some species.

<!-- consequences for conservation planning -->
+ Typically, conservation planning exercises do not consider intra-specific variation when designing prioritizations. 
+ our results show that for most species, a sufficient proportion of their intra-specific variation can be secured using suitable amount-based targets alone.
+ in particular, we found that using suitable amount-based targets in a multi-species context with comprehensive set of target species resulted in a prioritization that adequately represented the adaptive genetic variation for nearly all the target species (panel c; Figure 3).
+ however, for some species, such a prioritization secures only a small proportion of their genetic variation.
+ we found that for some species, prioritizations generated using amount-based targets only secured a small amount of their neutral genetic variation (panels b, d, e; Figure 3).
+ in planning exercises where the decision maker does not have access to genetic data on their target species across the extent of the study area--ie. nearly all real world planning scenarios--the decision maker will not know which species are poorly represented in terms of their inta-specific variation.
+ the poorly represented species may be those of particular significant or they may not.
+ the decision maker has to weigh the increased costs of a prioritization that includes environmental and geographic surrogates against the risk that a prioritization that does not include these surrogates fails to represent species of conservation significance.
+ here we found that prioritizations generated using environmental and geographic surrogates have only minor increased costs (compare panels c and d; panels e and f; Figure 3).
+ overall, these results suggest that although surrogates are unnecessary for most species, they can be highly beneficial for a few species, the increased costs associated with using these surrogates is small, so generally using surrogates is a good idea.

<!-- comparison to previous studies that have investigated genetic studies -->
+ Previous studies on this data set have found correlations between environmental and genetic variation.
+ Yet, for most species, prioritizations generated using environmental surrogates did not secure substantially more genetic variation than randomly generated prioritizations with the same number of planning units.
+ Here we discuss some potential reasons for this disagreement.
+

+ This apparent disagreement can be attributed to multiple reasons.

+ These results highlight the importance of using prioritizations to assess the effectiveness of potential surrogates for conservation and not simply measuring the strength of correlation between potential surrogates and genetic variation.

<!-- limitations/future directions -->
We wish to alert our readers to several limitations associated with our analysis. First, the size of the planning units we used (23 $\times$ 25 km) is much larger than typically used in conservation planning scenarios (between 1--10 km^2). We used this resolution because the genetic data was collected at this scale. Whilst we could have interpolated the genetic data to a finer resolution and used smaller planning units, this would have biased our analysis because this process would have  artificially introduced additional spatial auto-correlation into the dataset. Second, we used geographic distances as surrogates for connectivity between planning units. Although connectivity between areas can be modeled using isolation by resistance measures [@r473] derived from landscape data [eg. @r474], they are unlikely to be of use in broad-scale conservation exercises since they need to be tuned using species-specific parameters. Third, we used AFLP data to characterize the main gradients of genetic variation. Whilst next-generation sequencing provides higher resolution genetic information than AFLP data [reviewed in @r480], our methodology would still have utilized only the main gradients of the genetic variation in order to generate prioritizations in a feasible amount of time. Overall, we are confident that the limitations associated with our study are relatively minor.
